Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-17 scagnostics.Rmd
More comments.
Updated plot appearance.

```{r plotgrandtour, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on projections. Most of the indices exhibit sharp jumps in scagnostic value."}
fullResMelt <- melt(fullRes, id=c("t", "name", "size"))
ggplot(fullResMelt, aes(x=t, y=value)) +
  geom_line(aes(color=name, linetype=factor(size))) + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```

@@

```{r plannedgrandtour, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on projections. Most of the indices exhibit sharp jumps in scagnostic value."}
fullResMeltPlanned <- melt(fullResPlanned, id=c("t", "name", "size"))
ggplot(fullResMeltPlanned, aes(x=t, y=value)) +
  geom_line(aes(color=name, linetype=factor(size))) + 
  facet_wrap(~variable, ncol=1, scales = "free_y")

@@

TIC was suggested in @JMLRv1715308 as an alternative to MIC with better properties for testing against independence, this is because the full information of the characteristics is used, implying that more information is considered. We also see that TIC is smoother when moving into the special view.

>>>>

```{r plotgrandtour, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on projections. Most of the indices exhibit sharp jumps in scagnostic value."}
fullResMelt <- melt(fullRes, id=c("t", "name", "size"))
ggplot(fullResMelt, aes(x=t, y=value)) +
  geom_line(aes(color=factor(size))) + 
  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE)) +
  guides(color=FALSE)
```

@@

```{r plannedgrandtour, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on projections. Most of the indices exhibit sharp jumps in scagnostic value."}
fullResMeltPlanned <- melt(fullResPlanned, id=c("t", "name", "size"))
ggplot(fullResMeltPlanned, aes(x=t, y=value)) +
  geom_line(aes(color=factor(size))) + 
  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE)) +
  guides(color=FALSE)
```

@@

TIC was suggested in @JMLRv1715308 as an alternative to MIC with better properties for testing against independence, this is because the full information of the characteristics is used, implying that more information is considered. We also see that TIC is smoother when moving into the special view.
(As I understand TIC is however not equitable, i.e. it will prefer linear relations, and it may be instructive to optimise MIC and TIC)

FIXME need to check the MIC_e and TIC_e, supposedly faster computation and better discrimination!
